Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-06-30 main_new.tex
Updates from Overleaf

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary affiliation in an early version of this manuscript. The authors would also like to thank Niklas Linde of the University of Lausanne for providing constructive feedback on a version of the manuscript, and finally members of the AURLab for help with AUV deployments

>>>>

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary affiliation in an early version of this manuscript. The authors would also like to thank Niklas Linde of the University of Lausanne for providing constructive feedback about this work, and finally members of the AURLab for help with AUV deployments
